Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers

### 2016-07-04 notes/paper/paper.tex
Modifications to the title and abstract of the paper.

\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage[english]{babel}
\usepackage{pinyin}
\usepackage{natbib}
\usepackage{notoccite}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{floatrow}
\usepackage{amsmath}
%
\begin{document}
%
% paper title
\title{Real-Time Activity Classification by Match Filtering using Body-Worn Accelerometers}
%
\author{Craig~Euler, Bryan~Juarez, Melissa~Flores, C.T.~Lin}
%
\maketitle
%
\begin{abstract}
Having information of the user\textquotesingle s activity can provide great use in modern-day devices such as ones that track and monitor a user\textquotesingle s activity and fitness.
In this paper, we demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.
We also show the real-time processing capability of our algorithms on the MSP432P401R microcontroller.
Dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006} is a data compression technique we use to improve our processing throughput which, inherently, has the added benefit of making our data invariant to sensor orientation when applied.
Data decimation in time is an additional throughput enhancement that we apply early to our data.
We make use of an instance-based learning algorithm to train the device to learn the individual\textquotesingle s motion patterns and store that information as activity templates for use in our matched-filter.
\end{abstract}
%
\section{Introduction}
Various methods for activity classification using body-worn sensors exist.
Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
In this paper, we make use of the matched-filter method to identify an individual\textquotesingle s activity for the purpose of real-time processing.
The matched-filter method with use of thresholding and comparing the correlations of various filters is a simple method to use and has been studied in the past \cite{giannakis_tsatsanis_1990}.
The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller (we use the MSP432 microcontroller).

>>>>

\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage[english]{babel}
\usepackage{pinyin}
\usepackage{natbib}
\usepackage{notoccite}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{floatrow}
\usepackage{amsmath}
%
\begin{document}
%
% paper title
\title{Real-Time Activity Classification by Matched Filtering using Body-Worn Accelerometers}
%
\author{Craig~Euler, C.T.~Lin, Bryan~Juarez, Melissa~Flores}
%
\maketitle
%
\begin{abstract}
Having information of a user\textquotesingle s activity can provide great use in modern-day devices such as ones that track and monitor the user\textquotesingle s activity and fitness.
In this paper, we demonstrate activity classification performance of the matched-filtering method with data obtained from a three-axis accelerometer worn by the user.
We also show the real-time processing capability of our algorithms on the MSP432P401R microcontroller.
Dimensionality reduction with principal component analysis (PCA) \cite{bishop_2006} is a data compression technique we use to improve our processing throughput which, inherently, has the added benefit of making our data invariant to sensor orientation when applied.
Data decimation in time is an additional throughput enhancement that we apply early to our data.
We make use of an instance-based learning algorithm to train the device to learn the individual\textquotesingle s motion patterns and store that information as activity templates for use in our matched-filter.
\end{abstract}
%
\section{Introduction}
Various methods for activity classification using body-worn sensors exist.
Custom Decision Tree, Automatically Generated Decision Tree, and Artificial Neural Networks \cite{parkka_ermes_korpipaa_mantyjarvi_peltola_korhonen_2006} have been explored as well as other frequency based classification methods \cite{sharma_purwar_lee_lee_chung_2008}.
In this paper, we make use of the matched-filter method to identify an individual\textquotesingle s activity for the purpose of real-time processing.
The matched-filter method with use of thresholding and comparing the correlations of various filters is a simple method to use and has been studied in the past \cite{giannakis_tsatsanis_1990}.
The methods used for our algorithms are designed for computational efficiency to accommodate the resource limitations of a microcontroller (we use the MSP432 microcontroller).
